Principles for Open Data Curation: A Case Study with the New York City 311 Service Request Data

### 2024-06-14 manuscript/manuscript.tex
Update

Since the NYC 311 System went live in 2003, the usage has grown at an annual
rate of 4.6\%. As part of this study, we also looked at a 10-year period (2014-2023) to
observe system performance over a longer time-frame . During that time-frame, 
the number of 311 SRs grew 50\%.

\begin{figure}[tbp]
  \centering
  \caption{Yearly SR counts over 10-years}
  \includegraphics[width=\textwidth]{Yearly.pdf}
  \label{fig:yearly-counts}
\end{figure}

This 10-year timeframe (2014-2023) includes the COVID pandemic. INote that the pandemic
impact reached a peak in the July-September 2020 timeframe, accompanied by additional spikes
in the 2\textsuperscript{nd}half of 2021 as well. The all-time daily high for SRs occurred on Tuesday, 2020-08-04, 
with a spike of 24,415 SRs, a full 9.8 \textsigma's from the mean.

This chart shows the 2-year period which is the basis for this analysis, by calendar month. 
Note that almost all the months before the COVID pandemic outbreak in Feb/Mar
of 2020 are ``below average'', while most of the months after that period are ``above average''. That level of higher usage
of the 311 system has continued into the early months of 2024.

\begin{figure}[htbp]
  \centering
   \caption{Monthly SR counts over 10-years}
  \includegraphics[width=\textwidth]{10-year-monthly.pdf}
  \label{fig:monthly-counts}
\end{figure}

It is not surprising that the lowest SR counts-per-day occur during the Christmas holiday period. The summer months and early
fall months make up all of the Top 5 SR counts by day. (As a note, the all-time daily high for SRs occurred on Tuesday, 2020-08-04 while the 10-year
low count occurs on Christmas Day in 2016, a Sunday. Note also that the difference between the peak day (24,415) and the minimum day (2965) varies
by a factor of 8X; all of which creates a challenging  system capacity and performance issue.

\begin{table}[tbp]
    \centering
    \small
    \caption{Top 5 and Bottom 5 Days for SRs}
    \begin{tabular}{@{}lll lll@{}}
        \toprule
        \multicolumn{3}{c}{Top 5 Days} & \multicolumn{3}{c}{Bottom 5 Days} \\
        \cmidrule(r){1-3} \cmidrule(l){4-6}
        Date & Count & Rank & Date & Count & Rank \\
        \midrule
        2020-08-04 & 24,415 & 1 & 2014-12-25 & 2965 & 1 \\
        2020-08-05 & 19,560 & 2 & 2015-12-25 & 3247 & 2 \\
        2023-09-29 & 17,962 & 3 & 2014-04-20 & 3287 & 3 \\
        2020-07-05 & 16,916 & 4 & 2015-12-26 & 3405 & 4 \\
        2020-06-21 & 15,883 & 5 & 2016-11-06 & 3419 & 5 \\
        \bottomrule
    \end{tabular}
    \label{tab:combined_counts}
\end{table}

@@

\begin{figure}[tbp]
	\centering
  	\caption{SR counts by Agency and Cumulative Percentage}
	\includegraphics[width=\textwidth]{SRs_by_Agency.pdf}  
\end{figure}

@@

\begin{figure}[tbp]
  \centering
  	\caption{Top 20 SR complaint\_type and Cumulative Percentage}
	  \includegraphics[width=\textwidth]{SR_by_Complaint_Type.pdf}  
	  \label{fig:SR_complaints}
\end{figure}

@@

\begin{table}[tbp]
    \centering
    \caption{Noise-related complaints\_type(s) by count with Agency}
    \footnotesize
    \begin{tabular}{@{}lS[table-format=7.0,round-mode=places,round-precision=0]S[table-format=2.2,round-mode=places,round-precision=2]l@{}} % 'l' for left-aligned, 'S' for siunitx number alignment
        \toprule
        \textbf{complaint\_type} & \textbf{Count} & \textbf{Percentage} & \textbf{Agency} \\ 
        \midrule
        NOISE - RESIDENTIAL        & 675502 & 10.56 & NYPD  \\ 
        NOISE - STREET/SIDEWALK    & 300507 &  4.70 & NYPD  \\ 
        NOISE - COMMERCIAL         & 128892 &  2.02 & NYPD  \\ 
        NOISE - VEHICLE            & 115956 &  1.81 & NYPD  \\ 
        NOISE                      & 100413 &  1.57 & DEP   \\ 
        NOISE - HELICOPTER         &  85345 &  1.33 & EDC   \\ 
        NOISE - PARK               &  16620 &  0.26 & NYPD  \\ 
        NOISE - HOUSE OF WORSHIP   &   2757 &  0.04 & NYPD  \\ 
        \bottomrule
    \end{tabular}
    \label{tab:noisecomplaints}
\end{table}

@@

\begin{figure}[tbp]
  \centering
  \caption{Screenshot of data portal showing the ``@computed'' columns}
	  \includegraphics[width = 0.65\textwidth] {computed_columns_screenshot.pdf}	  
	  \label{fig:computed-columns}
\end{figure}

@@

\begin{table}[tbp]
\centering
\caption{Blank and N/A entries by Field}
\resizebox{0.8\linewidth}{!}{%
\scriptsize
\begin{tabular}{lrrrl}
	\toprule
	\textbf{Field} & \textbf{Total Empty} & \textbf{Percent Empty} & \textbf{N/A Count} \\
	\midrule
		taxi\_company\_borough & 6391341 & 99.94 & 0 \\
		road\_ramp & 6379080 & 99.75 & 0 \\
		vehicle\_type & 6376266 & 99.71 & 0 \\
		due\_date & 6370497 & 99.62 & 6370497 \\
		bridge\_highway\_direction & 6367626 & 99.57 & 0 \\
		bridge\_highway\_name & 6340197 & 99.14 & 0 \\
		bridge\_highway\_segment & 6340190 & 99.14 & 0 \\
		taxi\_pick\_up\_location & 6329954 & 98.98 & 0 \\
		facility\_type & 5966588 & 93.30 & 0 \\
		landmark & 2635736 & 41.22 & 0 \\
		intersection\_street\_1 & 2143847 & 33.52 & 0 \\
		intersection\_street\_2 & 2140707 & 33.48 & 0 \\
		cross\_street\_1 & 1846594 & 28.88 & 0 \\
		cross\_street\_2 & 1846008 & 28.87 & 0 \\
		location\_type & 798775 & 12.49 & 0 \\
		bbl & 768109 & 12.01 & 0 \\
		city & 332086 & 5.19 & 0 \\
		street\_name & 280463 & 4.39 & 0 \\
		incident\_address & 280268 & 4.38 & 0 \\
		closed\_date & 248839 & 3.89 & 248839 \\
		resolution\_description & 132333 & 2.07 & 0 \\
		zip\_codes & 123167 & 1.93 & 0 \\
		borough\_boundaries & 101453 & 1.59 & 0 \\
		community\_districts & 101445 & 1.59 & 0 \\
		city\_council\_districts & 101445 & 1.59 & 0 \\
		police\_precincts & 101445 & 1.59 & 0 \\
		police\_precinct & 101416 & 1.59 & 0 \\
		latitude & 99778 & 1.56 & 0 \\
		longitude & 99778 & 1.56 & 0 \\
		location & 99778 & 1.56 & 0 \\
		x\_coordinate\_state\_plane & 99668 & 1.56 & 0 \\
		y\_coordinate\_state\_plane & 98822 & 1.55 & 0 \\
		resolution\_action\_updated\_date & 91399 & 1.43 & 91399 \\
		incident\_zip & 83220 & 1.30 & 2 \\
		descriptor & 74645 & 1.17 & 0 \\
		address\_type & 38655 & 0.60 & 0 \\
		unique\_key & 0 & 0.00 & 0 \\
		agency & 0 & 0.00 & 0 \\
		agency\_name & 0 & 0.00 & 0 \\
		complaint\_type & 0 & 0.00 & 0 \\
		status & 0 & 0.00 & 0 \\
		community\_board & 0 & 0.00 & 0 \\
		borough & 0 & 0.00 & 0 \\
		open\_data\_channel\_type & 0 & 0.00 & 0 \\
		park\_facility\_name & 0 & 0.00 & 0 \\
		park\_borough & 0 & 0.00 & 0 \\
		created\_date & 0 & 0.00 & 0 \\
	\bottomrule
\end{tabular}
}
\end{table}

@@

\begin{table}[tbp]
    \centering
    \footnotesize
    \caption{Comparison of Top Ten Zip Codes Lists}
    \begin{tabular}{@{}lS[table-format=6.0,round-mode=places,round-precision=0]c@{\hskip 0.5cm}@{}lS[table-format=6.0,round-mode=places,round-precision=0]c@{}}
        \toprule
        \multicolumn{3}{c}{\textbf{zip\_codes}} & \multicolumn{3}{c}{\textbf{incident\_zip}} \\
        \cmidrule(r){1-3} \cmidrule(l){4-6}
        \textbf{Zip Code} & \textbf{Count} & \textbf{Valid?} & \textbf{Zip Code} & \textbf{Count} & \textbf{Valid?} \\
        \midrule
        11275 & 104556 & FALSE & 10466 & 104562 & TRUE \\
        12420 & 27503 & TRUE & 10023 & 27972 & TRUE \\
        12428 & 26564 & TRUE & 10031 & 25548 & TRUE \\
        10935 & 25508 & FALSE & 10457 & 25066 & TRUE \\
        10934 & 23448 & FALSE & 10453 & 24752 & TRUE \\
        10931 & 22381 & TRUE & 10456 & 24751 & TRUE \\
        10930 & 22121 & TRUE & 10452 & 22527 & TRUE \\
        17613 & 21963 & FALSE & 10025 & 21705 & TRUE \\
        10936 & 21707 & FALSE & 10458 & 21689 & TRUE \\
        11606 & 21435 & FALSE & 10032 & 20622 & TRUE \\
        \bottomrule
    \end{tabular}
    \label{tab:zipcodes}
\end{table}

@@

	\begin{table}[tbp]
	\footnotesize
	\centering
	\caption{Comparison of the fields police\_precinct and police\_precincts}
		\begin{tabular}{ccccc}
		\toprule
		\textbf{Invalid Precinct} & \textbf{police\_precinct count} & \textbf{police\_precincts count} & \textbf{Delta}\\
		\midrule
			62 & 151808 & 151720 & 88 \\
			72 & 148881 & 148796 & 85 \\
			67 & 133171 & 133115 & 56 \\
			64 & 111236 & 111221 & 15 \\
			60 & 105252 & 105317 & -65 \\
			65 & 103334 & 103306 & 28 \\
			53 & 100097 & 100074 & 23 \\
			73 & 97746 & 97755 & -9 \\
			68 & 94204 & 94254 & -50 \\
			66 & 93654 & 93848 & -194 \\
	\bottomrule
	\end{tabular}
	\label{tab:comparison-precincts-diff}
	\end{table}

@@

		\begin{table}[tbp]
		\centering
		\caption{Top Ten Invalid 'community\_board' Values}
		\footnotesize
		\begin{tabular}{rlr}
		\toprule
		\textbf{Rank} & \textbf{Invalid CB} & \textbf{Count} \\
			\midrule
				1 & 64 MANHATTAN & 7144 \\
				2 & 83 QUEENS & 5133 \\
				3 & 55 BROOKLYN & 3327 \\
				4 & 81 QUEENS & 3180 \\
				5 & 80 QUEENS & 2407 \\
				6 & 26 BRONX & 2364 \\
				7 & 28 BRONX & 1128 \\
				8 & 82 QUEENS & 1054 \\
				9 & 95 STATEN ISLAND & 515 \\
				10 & 27 BRONX & 514 \\
			\bottomrule
		\end{tabular}
		\end{table}

@@

\begin{table}[tbp]
    \centering
    \caption{Largest and Smallest errors (days)}
    \small
    \begin{tabular}{>{\ttfamily}l l l r l}
        \toprule
        \multicolumn{5}{c}{\textbf{Largest errors (days) excluding extreme negative values}} \\
        \midrule
        \textbf{created\_date} & \textbf{closed\_date} & \textbf{duration} & \textbf{agency} \\
	        \midrule
	        2023-01-27 14:40:00 & 2022-01-14 14:40:00 & -378.0 & DOT \\
	        2023-01-18 10:06:00 & 2022-01-12 10:06:00 & -371.0 & DOT \\
	        2023-01-27 14:36:00 & 2022-01-22 14:35:00 & -370.0 & DOT \\
	        2023-01-11 11:10:00 & 2022-01-09 11:10:00 & -367.0 & DOT \\
	        2023-12-18 03:13:00 & 2023-01-16 13:10:00 & -335.6 & DOT \\
	        \midrule
	        \multicolumn{5}{c}{\textbf{Smallest errors (days)}} \\
	        \midrule
	        \textbf{created\_date} & \textbf{closed\_date} & \textbf{duration} & \textbf{agency} \\
	        \midrule
	        2023-06-28 07:07:31 & 2023-06-28 07:07:00 & -0.00036 & DOT \\
	        2023-06-29 09:10:20 & 2023-06-29 09:10:00 & -0.00023 & DOT \\
	        2023-01-12 06:50:13 & 2023-01-12 06:50:00 & -0.00015 & DOT \\
	        2023-06-26 08:09:07 & 2023-06-26 08:09:00 & -0.00008 & DOT \\
	        2023-01-12 06:51:01 & 2023-01-12 06:51:00 & -0.00001 & DOT \\
	        \bottomrule
    \end{tabular}
    \label{tab:combined_errors}
\end{table}

@@

\begin{table}[tbp]
    \centering
    \caption{Sample of SRs with extremely large negative durations}
    \small
    \begin{tabular}{l l r l}
        \toprule
        \textbf{created\_date} & \textbf{closed\_date} & \textbf{duration} & \textbf{agency} \\
	        \midrule
	        2022-02-11 13:43:05 & 1900-01-01 & -44602 & DHS \\
	        2022-02-11 11:03:38 & 1900-01-01 & -44602 & DHS \\
	        2022-02-11 08:29:49 & 1900-01-01 & -44601 & DHS \\
	        2022-02-11 14:08:08 & 1900-01-01 & -44602 & DHS \\
	        2022-02-11 14:05:16 & 1900-01-01 & -44602 & DHS \\
	        \bottomrule
    \end{tabular}
    \label{tab:extreme_negative_durations}
\end{table}

@@

	\begin{figure}[tbp]
		 \centering
		  \caption{SRs with Zero Durations by Agency}
		 \includegraphics[width = \textwidth]{zero_duration_SR.pdf}
		 \label{fig:sero-duration}
	\end{figure}

@@

	\begin{figure}[tbp]
		 \centering
		 \caption{SRs by Hourly created\_date(s)}
		 \includegraphics[width = \textwidth]{Created_Hourly_SR_count.pdf}
		 \label{fig:hourly-created}
	\end{figure}

	\begin{figure}[tbp]
		 \centering
		 \caption{SRs by Hourly closed\_date(s)}
		 \includegraphics[width = \textwidth]{Closed_Hourly_SR_count.pdf}
		 \label{fig:hourly-closed}
	\end{figure}

@@

	\begin{figure}[tbp]
		 \centering
 		 \caption{SRs Created at Top of the Hour}
		 \includegraphics[width = \textwidth]{SR_created_by_top_of_hour.pdf}
		 \label{fig:tophourcreated}
	\end{figure}

@@

	\begin{figure}[tbp]
		 \centering
		 \caption{SRs created minute-by-minute on busiest day}
		 \includegraphics[width=\textwidth]{SR_created_by_minute_of_busiest_day.pdf}
		 \label{fig:busiestcreated}
	\end{figure}

@@

	\begin{figure}[tbp]
		 \centering
		 \caption{SRs Closed at Top of the Hour}
		 \includegraphics[width = \textwidth]{SR_closed_by_top_of_hour.pdf}
		 \label{fig:tophourclosed}
	\end{figure}

@@

 	\begin{figure}[tbp]
		 \centering
		  \caption{SRs closed minute-by-minute on busiest day}
		 \includegraphics[width=\textwidth]{SR_closed_by_minute_of_busiest_day.pdf}
		 \label{fig:busiestclosed}
	\end{figure}

@@

	Looking at the distribution by Agency for the ``closed-exactly-at-midnight'' shows that \textgreater{}90\% of these suspect SRs come from just two Agencies - Dept. of 
	Buildings (DOB) and Dept. of Sanitation (DSNY). If you include HPD and DOT, that accounts for 99\% of the suspect SR closures. This Agency
	distribution does not follow the overall SR distribution and we can assume that it is Agency specific.

	\begin{figure}[tbp]
		 \centering
		 \caption{SRs Closed Exactly at Midnight by Agency}
		 \includegraphics[width = \textwidth]{closed_at_midnight_chart.pdf}
		 \label{fig:midnight-closed}
	\end{figure}

	However, the ``SR closed at noon'' visualization shows that  a single Agency, DSNY,
	is responsible for \textgreater{}99\% of the SRs ``closed-exactly-at-noon''. Accordingly, any effort to resolve this issue
	necessitates working with DSNY to fully understand how this is occurring.

	\begin{figure}[tbp]
		 \centering
		  \caption{SRs Closed Exactly at Noon by Agency}
		 \includegraphics[width = \textwidth]{closed_at_noon_chart.pdf}
		 \label{fig:noon-closed}
	\end{figure}

	The 99,779 SRs created-exactly-at-noon also appears to originate with the Dept of Sanitation (DSNY) which
	is responsible for \textgreater{}99\% of the suspect SRs.

	\begin{figure}[tbp]
		 \centering
		 \caption{SRs Created Exactly at Noon by Agency}
		 \includegraphics[width = \textwidth]{created_at_noon_chart.pdf}
		 \label{fig:noon-created}
	\end{figure}

@@

	\begin{figure}[tbp]
		 \centering
		 \caption{Post-Closed resolution\_action\_update\_date >30 days by Agency }
		 \includegraphics[width = \textwidth]{postClosedBarChart.pdf}
		 \label{fig:resolution-by-agency}
	\end{figure}

@@

	\begin{figure}[tbp]
		 \centering
		  \caption{Non-matching borough and borough\_boundary by Agency }
		 \includegraphics[width = \textwidth]{non_matching_borough_boundaries_chart.pdf}
		 \label{fig:borough-boundaries}
	\end{figure}

>>>>

Since the NYC 311 System went live in 2003, the usage has grown at an annual
rate of 4.6\%. As part of this study, we also looked at a 10-year period (2014-2023) to
observe system performance over a longer time-frame . During that time-frame, 
the number of 311 SRs grew 50\%. The summer  and early fall months make up all of the Top 5 SR counts by day. 
The all-time daily high for SRs, 24,415 SRs (a full 9.8 \textsigma's from the 10-year mean), occurred on Tuesday, 2020-08-04.
The 10-year low count occurs on Christmas Day, 2016, a Sunday. Note also that the difference between 
the peak day (24,415) and the minimum day (2965) varies by 8X, creating a 
challenging system performance issue. This timeframe (2014-2023) also includes the COVID pandemic,  
which reached a peak in the July-September 2020 timeframe, 
accompanied by additional spikes in the 2\textsuperscript{nd}half of 2021 as well.

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{10-year-trend-monthly.pdf}
  \caption{Monthly SR counts over 10-years}
  \label{fig:10-yr-monthly}
\end{figure}

\begin{table}[tbp]
    \centering
    \normalsize
    \caption{Top 5 and Bottom 5 Days for SRs}
    \begin{tabular}{@{}lll lll@{}}
        \toprule
        \multicolumn{3}{c}{Top 5 Days} & \multicolumn{3}{c}{Bottom 5 Days} \\
        \cmidrule(r){1-3} \cmidrule(l){4-6}
        Date & Count & Rank & Date & Count & Rank \\
        \midrule
        2020-08-04 & 24,415 & 1 & 2014-12-25 & 2965 & 1 \\
        2020-08-05 & 19,560 & 2 & 2015-12-25 & 3247 & 2 \\
        2023-09-29 & 17,962 & 3 & 2014-04-20 & 3287 & 3 \\
        2020-07-05 & 16,916 & 4 & 2015-12-26 & 3405 & 4 \\
        2020-06-21 & 15,883 & 5 & 2016-11-06 & 3419 & 5 \\
        \bottomrule
    \end{tabular}
    \label{tab:top-10-counts}
\end{table}

This chart shows the 2-year period which is the basis for this analysis, by calendar month. 
Note that almost all the months before the COVID pandemic outbreak in Feb/Mar
of 2020 are ``below average'', while most of the months after that period are ``above average''. That level of higher usage
of the 311 system has continued into the early months of 2024. It is not surprising that the lowest SR counts-per-day occur during the Christmas holiday period.

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{2-year-trend-monthly.pdf}
  \caption{Monthly SR counts over years 2022-2023}
  \label{fig:2-yr-monthly}
\end{figure}

@@

\begin{figure}[tbp]
	\centering
	\includegraphics[width=\textwidth]{SRs_by_Agency.pdf}
  	\caption{SR counts by Agency and Cumulative Percentage}
	\label{fig:SRcountbyAgency}
\end{figure}

@@

\begin{figure}[tbp]
  \centering
 	\includegraphics[width=\textwidth]{SR_by_Complaint_Type.pdf} 
	\caption{Top 20 SR complaint\_type and Cumulative Percentage} 
	\label{fig:SR_complaints}
\end{figure}

@@

\begin{table}[tbp]
    \centering
    \caption{Noise-related complaints\_type(s) by count with Agency}
    \normalsize
    \begin{tabular}{@{}lS[table-format=7.0,round-mode=places,round-precision=0]S[table-format=2.2,round-mode=places,round-precision=2]l@{}} % 'l' for left-aligned, 'S' for siunitx number alignment
        \toprule
        \textbf{complaint\_type} & \textbf{Count} & \textbf{Percentage} & \textbf{Agency} \\ 
        \midrule
        NOISE - RESIDENTIAL        & 675502 & 10.56 & NYPD  \\ 
        NOISE - STREET/SIDEWALK    & 300507 &  4.70 & NYPD  \\ 
        NOISE - COMMERCIAL         & 128892 &  2.02 & NYPD  \\ 
        NOISE - VEHICLE            & 115956 &  1.81 & NYPD  \\ 
        NOISE                      & 100413 &  1.57 & DEP   \\ 
        NOISE - HELICOPTER         &  85345 &  1.33 & EDC   \\ 
        NOISE - PARK               &  16620 &  0.26 & NYPD  \\ 
        NOISE - HOUSE OF WORSHIP   &   2757 &  0.04 & NYPD  \\ 
        \bottomrule
    \end{tabular}
    \label{tab:noisecomplaints}
\end{table}

@@

\begin{figure}[tbp]
  \centering
 	\includegraphics[width = 0.65\textwidth] {computed_fields.pdf}	
	\caption{Screenshot of data portal showing the ``@computed'' columns}  
	\label{fig:computed-columns}
\end{figure}

@@

\begin{table}[tbp]
\centering
\caption{Blank and N/A entries by Field}
\resizebox{0.8\linewidth}{!}{%
\normalsize
\begin{tabular}{lrrrl}
	\toprule
	\textbf{Field} & \textbf{Total Empty} & \textbf{Percent Empty} & \textbf{N/A Count} \\
	\midrule
		taxi\_company\_borough & 6391341 & 99.94 & 0 \\
		road\_ramp & 6379080 & 99.75 & 0 \\
		vehicle\_type & 6376266 & 99.71 & 0 \\
		due\_date & 6370497 & 99.62 & 6370497 \\
		bridge\_highway\_direction & 6367626 & 99.57 & 0 \\
		bridge\_highway\_name & 6340197 & 99.14 & 0 \\
		bridge\_highway\_segment & 6340190 & 99.14 & 0 \\
		taxi\_pick\_up\_location & 6329954 & 98.98 & 0 \\
		facility\_type & 5966588 & 93.30 & 0 \\
		landmark & 2635736 & 41.22 & 0 \\
		intersection\_street\_1 & 2143847 & 33.52 & 0 \\
		intersection\_street\_2 & 2140707 & 33.48 & 0 \\
		cross\_street\_1 & 1846594 & 28.88 & 0 \\
		cross\_street\_2 & 1846008 & 28.87 & 0 \\
		location\_type & 798775 & 12.49 & 0 \\
		bbl & 768109 & 12.01 & 0 \\
		city & 332086 & 5.19 & 0 \\
		street\_name & 280463 & 4.39 & 0 \\
		incident\_address & 280268 & 4.38 & 0 \\
		closed\_date & 248839 & 3.89 & 248839 \\
		resolution\_description & 132333 & 2.07 & 0 \\
		zip\_codes & 123167 & 1.93 & 0 \\
		borough\_boundaries & 101453 & 1.59 & 0 \\
		community\_districts & 101445 & 1.59 & 0 \\
		city\_council\_districts & 101445 & 1.59 & 0 \\
		police\_precincts & 101445 & 1.59 & 0 \\
		police\_precinct & 101416 & 1.59 & 0 \\
		latitude & 99778 & 1.56 & 0 \\
		longitude & 99778 & 1.56 & 0 \\
		location & 99778 & 1.56 & 0 \\
		x\_coordinate\_state\_plane & 99668 & 1.56 & 0 \\
		y\_coordinate\_state\_plane & 98822 & 1.55 & 0 \\
		resolution\_action\_updated\_date & 91399 & 1.43 & 91399 \\
		incident\_zip & 83220 & 1.30 & 2 \\
		descriptor & 74645 & 1.17 & 0 \\
		address\_type & 38655 & 0.60 & 0 \\
		unique\_key & 0 & 0.00 & 0 \\
		agency & 0 & 0.00 & 0 \\
		agency\_name & 0 & 0.00 & 0 \\
		complaint\_type & 0 & 0.00 & 0 \\
		status & 0 & 0.00 & 0 \\
		community\_board & 0 & 0.00 & 0 \\
		borough & 0 & 0.00 & 0 \\
		open\_data\_channel\_type & 0 & 0.00 & 0 \\
		park\_facility\_name & 0 & 0.00 & 0 \\
		park\_borough & 0 & 0.00 & 0 \\
		created\_date & 0 & 0.00 & 0 \\
	\bottomrule
\end{tabular}
}
\end{table}

@@

\begin{table}[tbp]
    \centering
    \normalsize
    \caption{Comparison of Top Ten Zip Codes Lists}
    \begin{tabular}{@{}lS[table-format=6.0,round-mode=places,round-precision=0]c@{\hskip 0.5cm}@{}lS[table-format=6.0,round-mode=places,round-precision=0]c@{}}
        \toprule
        \multicolumn{3}{c}{\textbf{zip\_codes}} & \multicolumn{3}{c}{\textbf{incident\_zip}} \\
        \cmidrule(r){1-3} \cmidrule(l){4-6}
        \textbf{Zip Code} & \textbf{Count} & \textbf{Valid?} & \textbf{Zip Code} & \textbf{Count} & \textbf{Valid?} \\
        \midrule
        11275 & 104556 & FALSE & 10466 & 104562 & TRUE \\
        12420 & 27503 & TRUE & 10023 & 27972 & TRUE \\
        12428 & 26564 & TRUE & 10031 & 25548 & TRUE \\
        10935 & 25508 & FALSE & 10457 & 25066 & TRUE \\
        10934 & 23448 & FALSE & 10453 & 24752 & TRUE \\
        10931 & 22381 & TRUE & 10456 & 24751 & TRUE \\
        10930 & 22121 & TRUE & 10452 & 22527 & TRUE \\
        17613 & 21963 & FALSE & 10025 & 21705 & TRUE \\
        10936 & 21707 & FALSE & 10458 & 21689 & TRUE \\
        11606 & 21435 & FALSE & 10032 & 20622 & TRUE \\
        \bottomrule
    \end{tabular}
    \label{tab:zipcodes}
\end{table}

@@

	\begin{table}[tbp]
	\normalsize
	\centering
	\caption{Comparison of the fields police\_precinct and police\_precincts}
		\begin{tabular}{ccccc}
		\toprule
		\textbf{Invalid Precinct} & \textbf{police\_precinct count} & \textbf{police\_precincts count} & \textbf{Delta}\\
		\midrule
			62 & 151808 & 151720 & 88 \\
			72 & 148881 & 148796 & 85 \\
			67 & 133171 & 133115 & 56 \\
			64 & 111236 & 111221 & 15 \\
			60 & 105252 & 105317 & -65 \\
			65 & 103334 & 103306 & 28 \\
			53 & 100097 & 100074 & 23 \\
			73 & 97746 & 97755 & -9 \\
			68 & 94204 & 94254 & -50 \\
			66 & 93654 & 93848 & -194 \\
	\bottomrule
	\end{tabular}
	\label{tab:comparison-precincts-diff}
	\end{table}

@@

		\begin{table}[tbp]
		\centering
		\caption{Top Ten Invalid 'community\_board' Values}
		\normalsize
		\begin{tabular}{rlr}
		\toprule
		\textbf{Rank} & \textbf{Invalid CB} & \textbf{Count} \\
			\midrule
				1 & 64 MANHATTAN & 7144 \\
				2 & 83 QUEENS & 5133 \\
				3 & 55 BROOKLYN & 3327 \\
				4 & 81 QUEENS & 3180 \\
				5 & 80 QUEENS & 2407 \\
				6 & 26 BRONX & 2364 \\
				7 & 28 BRONX & 1128 \\
				8 & 82 QUEENS & 1054 \\
				9 & 95 STATEN ISLAND & 515 \\
				10 & 27 BRONX & 514 \\
			\bottomrule
		\end{tabular}
		\end{table}

@@

\begin{table}[tbp]
    \centering
    \caption{Largest and Smallest errors (days)}
    \normalsize
    \begin{tabular}{>{\ttfamily}l l l r l}
        \toprule
        \multicolumn{5}{c}{\textbf{Largest errors (days) excluding extreme negative values}} \\
        \midrule
        \textbf{created\_date} & \textbf{closed\_date} & \textbf{duration} & \textbf{agency} \\
	        \midrule
	        2023-01-27 14:40:00 & 2022-01-14 14:40:00 & -378.0 & DOT \\
	        2023-01-18 10:06:00 & 2022-01-12 10:06:00 & -371.0 & DOT \\
	        2023-01-27 14:36:00 & 2022-01-22 14:35:00 & -370.0 & DOT \\
	        2023-01-11 11:10:00 & 2022-01-09 11:10:00 & -367.0 & DOT \\
	        2023-12-18 03:13:00 & 2023-01-16 13:10:00 & -335.6 & DOT \\
	        \midrule
	        \multicolumn{5}{c}{\textbf{Smallest errors (days)}} \\
	        \midrule
	        \textbf{created\_date} & \textbf{closed\_date} & \textbf{duration} & \textbf{agency} \\
	        \midrule
	        2023-06-28 07:07:31 & 2023-06-28 07:07:00 & -0.00036 & DOT \\
	        2023-06-29 09:10:20 & 2023-06-29 09:10:00 & -0.00023 & DOT \\
	        2023-01-12 06:50:13 & 2023-01-12 06:50:00 & -0.00015 & DOT \\
	        2023-06-26 08:09:07 & 2023-06-26 08:09:00 & -0.00008 & DOT \\
	        2023-01-12 06:51:01 & 2023-01-12 06:51:00 & -0.00001 & DOT \\
	        \bottomrule
    \end{tabular}
    \label{tab:combined_errors}
\end{table}

@@

\begin{table}[tbp]
    \centering
    \caption{Sample of SRs with extremely large negative durations}
    \normalsize
    \begin{tabular}{l l r l}
        \toprule
        \textbf{created\_date} & \textbf{closed\_date} & \textbf{duration} & \textbf{agency} \\
	        \midrule
	        2022-02-11 13:43:05 & 1900-01-01 & -44602 & DHS \\
	        2022-02-11 11:03:38 & 1900-01-01 & -44602 & DHS \\
	        2022-02-11 08:29:49 & 1900-01-01 & -44601 & DHS \\
	        2022-02-11 14:08:08 & 1900-01-01 & -44602 & DHS \\
	        2022-02-11 14:05:16 & 1900-01-01 & -44602 & DHS \\
	        \bottomrule
    \end{tabular}
    \label{tab:extreme_negative_durations}
\end{table}

@@

	\begin{figure}[tbp]
		 \centering
		  \caption{SRs with Zero Durations by Agency}
		 \includegraphics[width = \textwidth]{zero_duration_SR.pdf}
		 \label{fig:zero-duration}
	\end{figure}

@@

	\begin{figure}[tbp]
		\centering
		\includegraphics[width = \textwidth]{Created_Hourly_SR_count.pdf}
		\caption{SRs by Hourly created\_date(s)}
		\label{fig:hourly-created}
	\end{figure}

	\begin{figure}[tbp]
		\centering
		\includegraphics[width = \textwidth]{Closed_Hourly_SR_count.pdf}
		\caption{SRs by Hourly closed\_date(s)}
		\label{fig:hourly-closed}
	\end{figure}

@@

	\begin{figure}[tbp]
		\centering
 		\includegraphics[width = \textwidth]{2-year-trend-SR_created_by_top_of_hour.pdf}
		\caption{SRs Created at Top of the Hour}
		\label{fig:tophourcreated}
	\end{figure}

@@

	\begin{figure}[tbp]
		\centering
		\includegraphics[width=\textwidth]{2-year-trend-SR_created_by_minute_of_busiest_day.pdf}
		\caption{SRs created minute-by-minute on busiest day}
		\label{fig:busiestcreated}
	\end{figure}

@@

	\begin{figure}[tbp]
		\centering
		\includegraphics[width = \textwidth]{2-year-trend-SR_closed_by_top_of_hour.pdf}
		\caption{SRs Closed at Top of the Hour}
		\label{fig:tophourclosed}
	\end{figure}

@@

 	\begin{figure}[tbp]
		\centering
		\includegraphics[width=\textwidth]{2-year-trend-SR_closed_by_minute_of_busiest_day.pdf}
		\caption{SRs closed minute-by-minute on busiest day}
		\label{fig:busiestclosed}
	\end{figure}

@@

	Looking at the distribution by Agency for the ``closed-exactly-at-midnight'' shows that \textgreater90\% of these suspect SRs come from just two Agencies - Dept. of 
	Buildings (DOB) and Dept. of Sanitation (DSNY). If you include HPD and DOT, that accounts for 99\% of the suspect SR closures. This Agency
	distribution does not follow the overall SR distribution and we can assume that it is Agency specific.

	\begin{figure}[tbp]
		\centering
		\includegraphics[width = \textwidth]{closed_at_midnight_chart.pdf}
		\caption{SRs Closed Exactly at Midnight by Agency}
		\label{fig:midnight-closed}
	\end{figure}

	However, the ``SR closed at noon'' visualization shows that  a single Agency, DSNY,
	is responsible for \textgreater99\% of the SRs ``closed-exactly-at-noon''. Accordingly, any effort to resolve this issue
	necessitates working with DSNY to fully understand how this is occurring.

	\begin{figure}[tbp]
		\centering
		\includegraphics[width = \textwidth]{closed_at_noon_chart.pdf}
		\caption{SRs Closed Exactly at Noon by Agency}
		\label{fig:noon-closed}
	\end{figure}

	The 99,779 SRs created-exactly-at-noon also appears to originate with the Dept of Sanitation (DSNY) which
	is responsible for \textgreater99\% of the suspect SRs.

	\begin{figure}[tbp]
		\centering
		\includegraphics[width = \textwidth]{created_at_noon_chart.pdf}
		\caption{SRs Created Exactly at Noon by Agency}
		\label{fig:noon-created}
	\end{figure}

@@

	\begin{figure}[tbp]
		\centering
		\includegraphics[width = \textwidth]{postClosedBarChart.pdf}
		\caption{Post-Closed resolution\_action\_update\_date \textgreater30 days by Agency}
		\label{fig:resolution-by-agency}
	\end{figure}

@@

	\begin{figure}[tbp]
		\centering
		\includegraphics[width = \textwidth]{non_matching_borough_boundaries_chart.pdf}
		\caption{Non-matching borough and borough\_boundary by Agency}
		\label{fig:borough-boundaries}
	\end{figure}
